---
title: "task 1"
author: "Sameer"
date: "2025-04-23"
output: html_document
---
## Task 1
Use the mtcars dataset in r demonstrate how to filter rows where the mpg is greater than  and arrange the results in descending order of hp using the dplyr:

## Including Library

First include the library dplyr which is used for data manipulation, providing a consistent set of verbs that help you solve the most common data manipulation challenges: mutate() adds new variables that are functions of existing variables. select() picks variables based on their names.

```{r}
library(dplyr)
```

# calling Dataset
```{r}
data(mtcars)
```
# prnting first five rows of dataset
```{r}
head(mtcars)
```

# filtering rows where mpg is greater than 20 and arranging them is descending order
filter will filter the data so that we can have only filtered dataset 
Arrange will arrange the dataset to be in descending order
```{r}
result<-mtcars %>%
  filter(mpg>20) %>%
  arrange(desc(hp))
```

```{r}
print(result)
```

```{r}
head(result)
```

